The effect of detector nonlinearity on \wfa\ PSF profiles for weak gravitational lensing measurements

### 2016-04-19 bias_from_NL.tex
fixed references

To obtain a functional model of NL as a function of signal, we use laboratory measurements\footnote{Performed at Caltech by R. Smith and collaborators.} of H2RG 1.7 $\mu$m cutoff detectors, which have the same basic design of the H4RG that will be used in the WFI but with 18 $\mu$m pixels. A constant flux source is illuminated on the detector, and the NL measurements are done by non-destructive sample-up-the-ramp (SUTR) readout at multiple times. The value of the first frame is subtracted, and then the \emph{mean} signal is fitted to a polynomial. These measurements show that the voltage relation for a measured signal $S$ is well fit by a quadratic function in the mean signal $\langle Q \rangle$ of the form:

@@

\textcolor{blue}{For this work, we use profiles with a simulated AB magnitude up to 18.3 for an exposure time of 168.1 seconds (expected for the HLS). The total flux of the profiles in each band is shown in Table 1, along with their peak value. When the profile is drawn on a pixelated postage stamp with a scale of $p=0.11$ arcseconds and placed on the center of the pixel\footnote{Note that the peak value is a function of the PSF profile centroid location within the pixel, as well as reolution. When drawing the PSF profiles in our simulations, we randomize the PSF centroid within the native scale pixel, as described in Section YYY.}, this particular magnitude produces a peak charge of $\sim 1e5$e$^{-}$ (Y106 band, see Table 1), which represents about 90\% of the typical pixel full well value assumed above.}

@@

Fig. \ref{f3} shows the fractional change in PSF size and the absolute error in PSF ellipticity as a function of the mean nonlinearity parameter $\beta$, for different bandpass filters at fixed AB magnitude of 18.3 in each band, consistent with the magnitude of brightest stars that will be usable for the HLS. The effect depends on flux, and hence its amplitude is the largest in the Y106 bandpass filter (\emph{c.f.}, Table 1). We note that the flux in the other bands will depend on the stellar spectral energy distribution (SED), and we would need to specify a particular SED to go from the reference band to other bands. For simplicity, we are performing our calculations based on a grid of AB magnitudes in different bands, as calculated by \gs\.

@@

Non-linearity measurements are usually performed by looking at signal as a function of exposure time at a constant flux (and subtracting dark frames at the appropriate times), which is sensible to any gain dependence on fluence. These measurements are normally subject to other effects such as inaccuracies in the readout time, persistence, reciprocity failure, and time-dependent changes in the electronic offset due to self-heating effects in the multiplexer. Despite these challenges, the mean non-linearity signal can usually be characterized to a precision of 5\textendash10$\%$. Thus it is not obvious that a typical NL calibration program will be sufficient for WL with \wf\ without more careful study and error budgeting.
Validation tests will therefore be crucial through the use of a facility such as the 
Precision Projector Laboratory (PPL, \citealt{seshadri13}, \citealt{shapiro13})\footnote{The PPL is a joint project between NASA Jet Propulsion Laboratory and Caltech which characterizes image sensors using laboratory emulations of astronomical data.} to ensure that voltage nonlinearity in the \wf\ H4RG detectors can be calibrated to the levels demanded by WL science.}\\

>>>>

To obtain a functional model of NL as a function of signal, we use laboratory measurements\footnote{Performed at Caltech by R. Smith and collaborators.} of H2RG 1.7 $\mu$m cutoff detectors, which have the same basic design of the H4RG that will be used in the WFI but with 18 $\mu$m pixels. A constant flux source is illuminated on the detector, and the NL measurements are done by non-destructive sample-up-the-ramp (SUTR) readout at multiple times. The value of the first frame is subtracted, and then the \emph{mean} signal is fitted to a polynomial. These measurements show that the voltage relation for a measured signal $S$ is well fit by a quadratic function in the signal $Q$ of the form:

@@

For this work, we use profiles with a simulated AB magnitude up to 18.3 for an exposure time of 168.1 seconds (expected for the HLS). The total flux of the profiles in each band is shown in Table 1, along with their peak value. When the profile is drawn on a pixelated postage stamp with a scale of $p=0.11$ arcseconds and placed on the center of the pixel\footnote{Note that the peak value is a function of the PSF profile centroid location within the pixel, as well as resolution. When drawing the PSF profiles in our simulations, we randomize the PSF centroid within the native scale pixel, as described in Section YYY.}, this particular magnitude produces a peak charge of $\sim 1e5$e$^{-}$ (Y106 band, see Table 1), which represents about 90\% of the typical pixel full well value assumed above.

@@

Fig. \ref{f3} shows the fractional change in PSF size and the absolute error in PSF ellipticity as a function of the mean nonlinearity parameter $\beta$, for different bandpass filters at fixed AB magnitude of 18.3 in each band, consistent with the magnitude of brightest stars that will be usable for the HLS. The effect depends on flux, and hence its amplitude is the largest in the Y106 bandpass filter (\emph{c.f.}, Table 1). We note that the flux in the other bands will depend on the stellar spectral energy distribution (SED), and we would need to specify a particular SED to go from the reference band to other bands. For simplicity, we are performing our calculations based on a grid of AB magnitudes in different bands, as calculated by \gs.

@@

Non-linearity measurements are usually performed by looking at signal as a function of exposure time at a constant flux (and subtracting dark frames at the appropriate times), which is sensible to any gain dependence on fluence. These measurements are normally subject to other effects such as inaccuracies in the readout time, persistence, reciprocity failure, and time-dependent changes in the electronic offset due to self-heating effects in the multiplexer. Despite these challenges, the mean non-linearity signal can usually be characterized to a precision of 5\textendash10$\%$. Thus it is not obvious that a typical NL calibration program will be sufficient for WL with \wf\ without more careful study and error budgeting.
Validation tests will therefore be crucial through the use of a facility such as the 
Precision Projector Laboratory (PPL, \citealt{seshadri13}, \citealt{shapiro13})\footnote{The PPL is a joint project between NASA Jet Propulsion Laboratory and Caltech which characterizes image sensors using laboratory emulations of astronomical data.} to ensure that voltage nonlinearity in the \wf\ H4RG detectors can be calibrated to the levels demanded by WL science.\\
